Mendelian randomization for causal inference in genome-wide association studies

### 2022-02-28 mr-review.Rmd
added refs & section header for bidirectional MR

@fang2021evaluating, working with data from the UK Biobank, found that SNP instruments 
derived from overlapping samples explained a higher proportion of the variance compared to 
those derived from non-overlapping samples. They surmise that block jackknife resampling MR
enables causal inference while avoiding bias due to overlapping samples.

@@

>>>>

@fang2021evaluating, working with data from the UK Biobank, found that SNP instruments 
derived from overlapping samples explained a higher proportion of the variance compared to 
those derived from non-overlapping samples. They argue that block jackknife resampling MR
enables causal inference while avoiding bias due to overlapping samples.

@@

@mounier_bias_2021
@hartwig_two-sample_2016
@lawlor_commentary_2016
@burgess_bias_2016

## Bi-directional causal inference with MR

@darrous_simultaneous_2021
